---
title: "PCAPlots_ECR"
output: html_document
date: "2024-10-30"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
```


Code to make a single PCA plot is below. Please save your own version of this file and edit to make PCA plots for all the different PCA analyses generated in the original assignment.
```{r}
## read in PC data
## CHANGE THESE PATHS TO YOUR OWN DATA
mypcs <- read.table('path')

##make some sensible names
names(mypcs)[1:12] <- c('code','ID','PC1','PC2','PC3','PC4','PC5','PC6','PC7','PC8','PC9','PC10')

## read in data about arabidopsis
mydat <- read.table('~/plb812/genomic-data/accessions.csv', header=F, sep=",")
#make some sensible names again
names(mydat)[1] <- "ID"
names(mydat)[11] <- "region"

## join files together
myall <- dplyr::left_join(mypcs, mydat, by="ID")

## make a PC plot with PCs 1 and 2
ggplot(myall, aes(x=PC1, y=PC2, color=region))+
  geom_point()+
  theme_minimal()

##make a PC plot with PCs 3 and 4
ggplot(myall, aes(x=PC3, y=PC4, color=region))+
  geom_point()+
  theme_minimal()
```

```{r}
#Starting with the huge first eigenval file
#completely unfiltered
mypcs <- read.table('/mnt/home/rosseli5/08_PCA/arabidopsis-pca.eigenvec')

##make some sensible names
#Add proper headers
names(mypcs)[1:12] <- c('code','ID','PC1','PC2','PC3','PC4','PC5','PC6','PC7','PC8','PC9','PC10')

## read in data about arabidopsis
mydat <- read.table('/mnt/research/PLB812_FS24_S001/12_PCA/accessions.csv', header=F, sep=",")
#make some sensible names again
names(mydat)[1] <- "ID"
names(mydat)[11] <- "region"

## join files together
myall <- dplyr::left_join(mypcs, mydat, by="ID")

## make a PC plot with PCs 1 and 2
ggplot(myall, aes(x=PC1, y=PC2, color=region))+
  geom_point()+
  theme_minimal()

##make a PC plot with PCs 3 and 4
ggplot(myall, aes(x=PC3, y=PC4, color=region))+
  geom_point()+
  theme_minimal()

```

``````{r}
#100 SNPS
mypcs100 <- read.table('/mnt/home/rosseli5/08_PCA/arabidopsis100-pca.eigenvec')

##make some sensible names
#Add proper headers
names(mypcs100)[1:12] <- c('code','ID','PC1','PC2','PC3','PC4','PC5','PC6','PC7','PC8','PC9','PC10')

## read in data about arabidopsis
mydat <- read.table('/mnt/research/PLB812_FS24_S001/12_PCA/accessions.csv', header=F, sep=",")
#make some sensible names again
names(mydat)[1] <- "ID"
names(mydat)[11] <- "region"

## join files together
myall100 <- dplyr::left_join(mypcs100, mydat, by="ID")

## make a PC plot with PCs 1 and 2
ggplot(myall100, aes(x=PC1, y=PC2, color=region))+
  geom_point()+
  theme_minimal()

##make a PC plot with PCs 3 and 4
ggplot(myall100, aes(x=PC3, y=PC4, color=region))+
  geom_point()+
  theme_minimal()
```

``````{r}
#100 SNPS
mypcs1000 <- read.table('/mnt/home/rosseli5/08_PCA/arabidopsis1000-pca.eigenvec')

##make some sensible names
#Add proper headers
names(mypcs1000)[1:12] <- c('code','ID','PC1','PC2','PC3','PC4','PC5','PC6','PC7','PC8','PC9','PC10')

## read in data about arabidopsis
mydat <- read.table('/mnt/research/PLB812_FS24_S001/12_PCA/accessions.csv', header=F, sep=",")
#make some sensible names again
names(mydat)[1] <- "ID"
names(mydat)[11] <- "region"

## join files together
myall1000 <- dplyr::left_join(mypcs1000, mydat, by="ID")

## make a PC plot with PCs 1 and 2
ggplot(myall1000, aes(x=PC1, y=PC2, color=region))+
  geom_point()+
  theme_minimal()

##make a PC plot with PCs 3 and 4
ggplot(myall1000, aes(x=PC3, y=PC4, color=region))+
  geom_point()+
  theme_minimal()
```

``````{r}
#100 SNPS
mypcs10000 <- read.table('/mnt/home/rosseli5/08_PCA/arabidopsis10000-pca.eigenvec')

##make some sensible names
#Add proper headers
names(mypcs10000)[1:12] <- c('code','ID','PC1','PC2','PC3','PC4','PC5','PC6','PC7','PC8','PC9','PC10')

## read in data about arabidopsis
mydat <- read.table('/mnt/research/PLB812_FS24_S001/12_PCA/accessions.csv', header=F, sep=",")
#make some sensible names again
names(mydat)[1] <- "ID"
names(mydat)[11] <- "region"

## join files together
myall10000 <- dplyr::left_join(mypcs10000, mydat, by="ID")

## make a PC plot with PCs 1 and 2
ggplot(myall10000, aes(x=PC1, y=PC2, color=region))+
  geom_point()+
  theme_minimal()

##make a PC plot with PCs 3 and 4
ggplot(myall10000, aes(x=PC3, y=PC4, color=region))+
  geom_point()+
  theme_minimal()
```